---
title: "Final Exam"
author: "OmarHassuneh"
date: "March 17, 2016"
output: html_document
---
```{r,warning=FALSE,message=FALSE}
library ("RSQLite")
library ("dplyr") 
library ("nycflights13")
library("ggplot2")

DataBase <- src_sqlite("my.sqlite2", create = T)

flights_sqlite <- copy_to(
  DataBase, flights, temporary = FALSE, 
  indexes = list(
    c("year", "month", "day"), 
    "carrier", 
    "tailnum")
)
airports_sqlite <- copy_to(
  DataBase, airports, temporary = FALSE, 
  indexes = list("faa")
)


airlines_sqlite <- copy_to(
  DataBase, airlines, temporary = FALSE, 
  indexes = list("carrier")
)


weather_sqlite <- copy_to(
  DataBase, weather, temporary = FALSE, 
  indexes = list(
    c("year", "month","day","hour"),
    "origin")
)


planes_sqlite <- copy_to(
  DataBase, planes, temporary = FALSE, 
  indexes = list("tailnum")
)


nycflights13_sqlite()
DataBase

flights_sqlite <- tbl(DataBase, "flights")
flights_sqlite

flights = tbl(DataBase, "flights") %>% 
  collect() %>%
  mutate(canceled = is.na(arr_time))

```

A. depature
a) weather 
```{r,warning=FALSE,message=FALSE}
flights_weather <- left_join(
  tbl(DataBase, "flights"),
  tbl(DataBase, "weather"),
  by = "origin")

reg_delay_temp<-lm(dep_delay~temp+dewp+humid+wind_dir+wind_speed+pressure,flights_weather)
summary(reg_delay_temp)
```
Just pressure in this regression is 90% significant.

b) time of day, day of week, and time of year, and any other aspect of time
```{r,warning=FALSE,message=FALSE}
flights_day <- tbl(DataBase, "flights") %>%
  group_by(day) %>%
  summarize(
    avg_delay = mean(dep_delay)   
  )%>%collect()

flights_day<-data.frame(flights_day)
p<- ggplot(flights_day, aes(x= factor(day),y=avg_delay)) + geom_bar(stat="identity", fill = "red")
p
flights_month <- tbl(DataBase, "flights") %>%
  group_by(month) %>%
  summarize(
    avg_delay = mean(dep_delay)   
  )%>%collect()

flights_month<-data.frame(flights_month)
p<- ggplot(flights_month, aes(x= factor(month),y=avg_delay)) + geom_bar(stat="identity", fill = "red")
p
```
Only 2013 in data, we can not analyze the dep_delay of year. We can tell that in June and July always get dep_delay.
But May get the smallest number of dep_delay.
The dep_delay is keep changing.

3.destination
```{r,warning=FALSE,message=FALSE}
f_a <- left_join(
  tbl(DataBase, "flights"),
  tbl(DataBase, "airports"),
  by = c("dest"="faa"))

f_a<-data.frame(f_a)
f_a_1 <- f_a %>%
  group_by(faa) %>%
  summarize(
    delaymean = mean(dep_delay,na.rm = T)    
  ) 
p<- ggplot(f_a_1, aes(x= factor(faa),y=delaymean))+geom_bar(stat="identity", fill = "red")
p
```
From the graph,In all those destinations, LEX planes arrive earliest.
But SBN get  departure delay is the higest.

4.planes
```{r,warning=FALSE,message=FALSE}
f_p <- left_join(
  tbl(DataBase, "flights"),
  tbl(DataBase, "planes"),
  by = "tailnum")

f_p<-data.frame(f_p)
f_p_1 <- f_p %>%
  group_by(manufacturer) %>%
  summarize(
    delaymean = mean(dep_delay,na.rm = T)    
  )

p <- ggplot(f_p_1, aes(x= factor(manufacturer),y=delaymean)) + geom_bar(stat="identity", fill = "red")+ theme(axis.text.x=element_text(angle = 90))
p
```
From the graph, I can tell that HURLEY JAMES LARRY get the lowest departure.
but planes in AGUSTA SPA always delay.

Part B cancelation
1.
```{r,warning=FALSE,message=FALSE}
c_w <- flights_sqlite %>% left_join(weather, by = "origin", copy = TRUE) %>% mutate(canceled = is.na(arr_time))

c_w<-data.frame(c_w)

g_p<- lm(canceled~pressure,c_w)
summary(g_p)
```

2.
```{r,warning=FALSE,message=FALSE}
flights_canceled = tbl(DataBase, "flights") %>% 
  collect() %>%
  mutate(canceled = is.na(arr_time))

flights_canceled<-data.frame(flights_canceled)

f_c <- flights_canceled %>%
  group_by(month) %>%
  summarize(
    canceled = sum(canceled)    
  ) 


p <- ggplot(f_c, aes(x= factor(month),y=canceled)) + geom_bar(stat="identity")
p

f_d <- flights_canceled %>%
  group_by(day) %>%
  summarize(
    canceled = sum(canceled)    
  ) 

p <- ggplot(f_d, aes(x= factor(day),y=canceled)) + geom_bar(stat="identity")
p
```
February alawys cancel the plane,which is very higher than the other month.
and on 8th of a month alway cancel the planes.

3.destination
```{r,warning=FALSE,message=FALSE}
f_e <- flights_sqlite %>% left_join(airports, by = c("dest"="faa"), copy = TRUE) %>% mutate(canceled = is.na(arr_time))

f_e<-data.frame(f_e)

f_g <- f_e %>%
  group_by(faa) %>%
  summarize(
    canceled = sum(canceled,na.rm = T)    
  ) 
p <- ggplot(f_g, aes(x= factor(faa),y=canceled)) + geom_bar(stat="identity")+theme(axis.text.x=element_text(angle = 75))
p
```
The destination which name is DCA always cancel all the planes.